Carbonate chemistry at Ny-Ålesund

### 2021-05-14 awipev-CO2.Rmd
finalized wind speed

load(file = paste0(path, "meteo_awi/wind_nyalesund.RData")) 
meteo <- tibble(windnyalesund) %>%
  dplyr::mutate(datetime = as_datetime(paste(paste(Year, Month, Day, sep="-"), paste(Hour, "00", "00", sep="-"), sep = " ")),
         temp_air = `Temperature[degC]`,
         p_air = `Pressure[hPa]`,
         ws = `WindSpeed[m/s]`,
         wd = `WindDirection[deg]`
        ) %>%
  dplyr::select(datetime, temp_air, p_air, ws, wd)
zz <- dplyr::left_join(d_all, meteo, by = "datetime") %>% 
  select(sort(current_vars()))
```

@@

##TO DO: check calculations by Miller et al. (2020); use formulation of Wanninkhof 2014?
d_all <- d_all %>%
  dplyr::mutate(delta_pco2 = pco2_fb - pco2_air, # ppm
                k600 = 0.266 * ws^2, #cm/hr Ho et al. (2006)
                Sc = 2073.1 - (125.62*temp_insitu_11m) + (3.6276*temp_insitu_11m^2) - (0.043219*temp_insitu_ctd^3), #dimensionless
                k = k600 * (Sc/600)^-0.5, #cm/h
                alp = seacarb::K0(S=sal_mix,T=temp_insitu_11m,P=0,Patm=p_air/1013.25), #mol/(kg/atm)
                alp = alp * (seacarb::rho(S = sal_mix, T = temp_insitu_11m, P = 0)/1000), #mol/(l/atm)
                f_air_sea = k * alp * delta_pco2 # mmol/(m2 h)
                )

p_f_air_sea <- ggplot(data=d_all) +
  geom_point(aes(x = datetime, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
  labs(title = "Air-sea CO2 flux (all data)", x = "Time", y = "CO2 (mmol/(m2 h))") +
  Mytheme(size_labs = 8)
#p_f_air_sea
#ggsave(filename = "figures/f_air_sea.png", plot = f_air_sea, width = 20, units = "cm")

>>>>

load(file = paste0(path, "meteo_awi/wind_nyalesund.RData")) 
meteo <- tibble(windnyalesund) %>%
  dplyr::mutate(datetime = as_datetime(paste(paste(Year, Month, Day, sep="-"), paste(Hour, "00", "00", sep="-"), sep = " ")),
         temp_air = `Temperature[degC]`,
         p_air = `Pressure[hPa]`,
         ws = `WindSpeed[m/s]`,
         wd = `WindDirection[deg]`
        ) %>%
  dplyr::select(datetime, temp_air, p_air, ws, wd)
d_all <- dplyr::left_join(d_all, meteo, by = "datetime") %>% 
  select(sort(current_vars()))
```

@@

##TO DO: check calculations by Miller et al. (2020); use formulation of Wanninkhof 2014?
d_all <- d_all %>%
  dplyr::mutate(delta_pco2 = pco2_fb - co2_air, # ppm
                k600 = 0.266 * ws^2, #cm/hr Ho et al. (2006)
                Sc = 2073.1 - (125.62*temp_insitu_11m) + (3.6276*temp_insitu_11m^2) - (0.043219*temp_insitu_ctd^3), #dimensionless
                k = k600 * (Sc/600)^-0.5, #cm/h
                alp = seacarb::K0(S=sal_mix,T=temp_insitu_11m,P=0,Patm=p_air/1013.25), #mol/(kg/atm)
                alp = alp * (seacarb::rho(S = sal_mix, T = temp_insitu_11m, P = 0)/1000), #mol/(l/atm)
                f_air_sea = k * alp * delta_pco2 # mmol/(m2 h)
                )

p_f_air_sea <- ggplot(data = d_all) +
  geom_point(aes(x = datetime, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
  labs(title = "Air-sea CO2 flux (all data)", x = "Time", y = "CO2 (mmol/(m2 h))") +
  Mytheme(size_labs = 8)
#p_f_air_sea
#ggsave(filename = "figures/f_air_sea.png", plot = f_air_sea, width = 20, units = "cm")
